---
title: "ECO395 HW1_Yuxin Feng_Jiyou Chen_Liming Pang"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>
<br>
<br>

# Question1 - Flights at ABIA

<br>

#### <font color = darkslateblue>Library several packages we will need.</font>

<br>

```{r}
library(tidyverse)
library(mosaic)
library(ggplot2)
library(data.table)
library(rsample)
library(caret)
library(modelr)
library(parallel)
library(foreach)
```

<br>

### Question a: What's the best time of year to fly to minimize delays?

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}
ABIA = read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/ABIA.csv")
# What is the best time of day to fly to minimize delays? 
ABIA %>%
  summarize(mean_DepDelay = mean(DepDelay))
ABIA %>% 
  summarize(favstats(DepDelay))
ABIA %>%
  summarize(mean_DepDelay = mean(DepDelay, na.rm=TRUE))

by_monthly_uniquecarrier = ABIA %>% 
  group_by(Month, UniqueCarrier) %>% 
  summarize(count = n(),
            mean_DepDelay = mean(DepDelay, na.rm=TRUE))
```


```{r, echo=FALSE,message=FALSE, warning=FALSE}
by_monthly_uniquecarrier
ggplot(by_monthly_uniquecarrier) + geom_col(aes(x=factor(Month), y=mean_DepDelay))
```

<br>

#### <font color = darkslateblue>Answer:</font>
#### <font color = darkslateblue>The chart below shows that December is the worst time to fly since the highest mean-delay.</font>

<br>
 
<br>

### Question b: Does the best time to fly to min delays change by destination?

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}
ggplot(by_monthly_uniquecarrier) + 
  geom_col(aes(x=factor(Month), y=mean_DepDelay)) + 
  facet_wrap(~UniqueCarrier)
```

<br>

#### <font color = darkslateblue>Answer:</font>
#### <font color = darkslateblue>Yes. Different airlines have different situation (shown in the last table). Take AA as example, the worst month is June apparently.</font>
<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}
by_monthly_uniquecarrier %>% 
  group_by(UniqueCarrier) %>%
  slice_max(order_by = mean_DepDelay, n=1)
```
<br>
<br>
<br>
<br>

# Question2 - Wrangling the Billboard Top100
<br>

## Part A

<br>

### Top 10 songs since 1958

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}
billboard <- read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/billboard.csv", row.names=1)
billboard_select = select(billboard, performer, song)
bb = count(billboard_select, performer, song) %>% arrange(desc(n))
colnames(bb) = c("performer", "song", "count")
billboard_top10 = bb[1:10,]

setDT(billboard_top10)
print (billboard_top10)
knitr::kable(billboard_top10,
             caption = "This is the top 10 songs since 1958 on Billboard!")

```

<br>

## Part B

<br>

### Musical Diversity Trend

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

billboard_select2 = select(billboard, song_id, year)
bb_diversity_unorganized1 = distinct(billboard_select2, song_id, year) %>% 
  arrange(year)
bb_diversity_unorganized2 = count(bb_diversity_unorganized1, year)
colnames(bb_diversity_unorganized2) = c("year","numbers")
n = nrow(bb_diversity_unorganized2)
billboard_diversity_by_year = bb_diversity_unorganized2[2:n-1,]

bbpicture = ggplot(data = billboard_diversity_by_year) + 
  geom_point(aes(x = year, y = numbers)) +
  geom_line(aes(x = year, y = numbers), size = 0.5, color = "Orange")
bbpicture + xlab("year(1589-2020)") + 
  ylab("Musical Diversity") +
  ggtitle("Billboard Musical Diversity Changes by year")

```

<br>

#### <font color = darkslateblue> Conclusion:</font>
#### <font color = darkslateblue> Once Billboard was introduced to the public, the diversity of music goes up very quickly until reached the peak in the 1960s, then it starts to go down for a long time and reached the lowest point around the start of the 2020s. After that, it appeared to go up again.</font>

<br>

## Part C

<br>

### Nineteen Artists with over 30 "ten-week-hit" songs

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

ten_week_hit = bb <- filter(bb, bb$count >= 10) %>% arrange(performer)
new_list = count(ten_week_hit, performer) %>% arrange(desc(n))
excellent_artists  = new_list[1:19,]

singer_pic = ggplot(data = excellent_artists, 
                    mapping = aes(x = performer, y = n, fill = performer))
singer_pic + geom_col() +
  xlab("Singers with 30+ 'Ten-Week-Hit' Songs") + 
  ylab("Number of Songs on Billboard for over 10 weeks") +
  ggtitle("Legendary Artists in Billboard History") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```

<br>
<br>
<br>
<br>

# Question3 - Wrangling the Olympics

<br>

## Part A

<br>

### 95 Percentile of Heignts for Female Competitors

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}
olympics_top20 = read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/olympics_top20.csv")
olympics_top20_Female = olympics_top20 %>% 
  filter(sex == "F")
head(olympics_top20_Female)
olympics_top20_Female %>% summarize(q95_height = quantile(height, 0.95)) %>% round(3)

```

<br>

#### <font color = darkslateblue> Female Competitor's 95 percentile height is 186.</font>

<br>

## Part B

<br>

### Women's Event with the Greatest Variability in Competitor's Height

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

olympics_top20_Female %>%
  group_by(event) %>%
  summarize(sd_height = sd(height)) %>% summarize(event=event[which.max(sd_height)],max_sd=max(sd_height, na.rm = TRUE))

```

<br>

#### <font color = darkslateblue> “Rowing Women's Coxed Fours” has the greatest women height variability.</font>

<br>

## Part C

<br>

### Average Age of Olympic Swimmers Trend

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

olympics_top20_swimmers = olympics_top20 %>% 
  filter(sport == "Swimming")


df_m_c <- data.frame(olympics_top20 %>% 
                       filter(sport == "Swimming", sex == "M" ) %>%
                       group_by(year) %>%
                       summarize(avg_age = mean(age, na.rm = TRUE)) %>%
                       round(3))


df_f_c <- data.frame(olympics_top20 %>%
                       filter(sport == "Swimming", sex == "F" ) %>%
                       group_by(year) %>%
                       summarize(avg_age = mean(age, na.rm = TRUE)) %>%
                       round(3))


df_all <- olympics_top20 %>% select(sex, age, year, sport) %>%
                      filter(sport == "Swimming") %>% 
                      group_by(year, sex) %>%
                      summarize(avg_age = mean(age, na.rm = TRUE))


ggplot(NULL,aes(year, avg_age)) +
  geom_line(data = df_m_c, col = "red") +
  geom_line(data = df_f_c, col = "blue") + labs(x = "Years", y = "Age", title = "Trend of Swimmers")
```

<br>

#### <font color = darkslateblue> Concllusion: The trend bewteen male and female competitors is different. Female competitor's ages are usually bigger than male's. Both average ages began to increase gradually since 1950.</font>

<br>
<br>
<br>
<br>

# Question4 - k-Nearest Neighbors

<br>

### Predictive Model

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

sclass = read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/sclass.csv")
sclass_350 = sclass %>% 
  filter(trim == "350") %>% select("mileage", "price")

sclass_65 = sclass %>% 
  filter(trim == "65 AMG") %>% select("mileage", "price")

sclass_350_split =  initial_split(sclass_350, prop=0.8)
sclass_350_train = training(sclass_350_split)
sclass_350_test  = testing(sclass_350_split)

sclass_65_split =  initial_split(sclass_65, prop=0.8)
sclass_65_train = training(sclass_65_split)
sclass_65_test  = testing(sclass_65_split)

lm_350 = lm(price ~ mileage, data=sclass_350_train)
lm_65 = lm(price ~ mileage, data=sclass_65_train)


K_folds = 10

sclass_350_folds = crossv_kfold(sclass_350, k=K_folds)
sclass_65_folds = crossv_kfold(sclass_350, k=K_folds)


sclass_350_models = map(sclass_350_folds$train, ~ knnreg(price ~ mileage, k=100, data = ., use.all=FALSE))
sclass_65_models = map(sclass_65_folds$train, ~ knnreg(price ~ mileage, k=100, data = ., use.all=FALSE))


sclass_350_rmse = map2_dbl(sclass_350_models, sclass_350_folds$test, modelr::rmse)
mean(sclass_350_rmse)
sclass_65_rmse = map2_dbl(sclass_350_models, sclass_65_folds$test, modelr::rmse)
mean(sclass_65_rmse)


k_grid = c(2, 4, 6, 8, 10, 15, 20, 25, 30, 35, 40, 45,
           50, 60, 70, 80, 90, 100, 125, 150, 175, 200, 250, 300)


sclass_350_grid = foreach(k = k_grid, .combine='rbind') %dopar% {
  models = map(sclass_350_folds$train, ~ knnreg(price ~ mileage, k=k, data = ., use.all=FALSE))
  sclass_350_rmse = map2_dbl(models, sclass_350_folds$test, modelr::rmse)
  c(k=k, err = mean(sclass_350_rmse))
} %>% as.data.frame

sclass_65_grid = foreach(k = k_grid, .combine='rbind') %dopar% {
  models = map(sclass_65_folds$train, ~ knnreg(price ~ mileage, k=k, data = ., use.all=FALSE))
  sclass_65_rmse = map2_dbl(models, sclass_65_folds$test, modelr::rmse)
  c(k=k, err = mean(sclass_65_rmse))
} %>% as.data.frame

```

<br>

### 350's AMG

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

ggplot(sclass_350_grid) + 
  geom_line(aes(x=k, y=err)) + labs(x = "k", y = "RMSE_350", title = "350") +
  scale_x_log10()

```

<br>

#### <font color = darkslateblue> From the picture we guess that RMSE_350 reaches its bottom when k is in [10,20].</font>

<br>

### 65's AMG

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

ggplot(sclass_65_grid) + 
  geom_line(aes(x=k, y=err)) + labs(x = "k", y = "RMSE_65", title = "65") +
  scale_x_log10()

```


<br>

#### <font color = darkslateblue> From the picture we guess that RMSE_65 reaches its bottom when k is in [10,20].</font>

<br>

### Calculating 350's and 65's AMG optimal k value

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}
min_k_350 <- sclass_350_grid %>% summarize(k=k[which.min(err)])
print(min_k_350)
min_k_65 <- sclass_65_grid %>% 
  summarize(k=k[which.min(err)])
print(min_k_65)
```

<br>

#### <font color = darkslateblue> Optimal k's for 350's and 65's are both 15.</font>

<br>

### sclass_350_test

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

knn350 = knnreg(price ~ mileage, data=sclass_350_train, k=min_k_350[1,1])
rmse(knn350, sclass_350_test)

sclass_350_test = sclass_350_test %>%
  mutate(price_pred = predict(knn350, sclass_350_test))

test_350 = ggplot(data = sclass_350_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)
test_350

test_350 + geom_line(aes(x = mileage, y = price_pred), color='red', size=1.5)

```

<br>

### sclass_65_test

<br>

```{r, echo=FALSE,message=FALSE, warning=FALSE}

knn65 = knnreg(price ~ mileage, data=sclass_65_train, k=min_k_65[1,1])
rmse(knn65, sclass_65_test)

sclass_65_test = sclass_65_test %>%
  mutate(price_pred = predict(knn65, sclass_65_test))

test_65 = ggplot(data = sclass_65_test) + 
  geom_point(mapping = aes(x = mileage, y = price), alpha=0.2)
test_65

test_65 + geom_line(aes(x = mileage, y = price_pred), color='blue', size=1.5)

```

<br>

#### <font color = darkslateblue> Two trims yields the same optimal k value. This mignt be because in this kind of situations, not mather the car's trim level changes, k = 15 is always the optimal value for doing KNN. Car's trim level might not be an influential factor .</font>


<br>
<br>
